AIR4Children: Artificial Intelligence and Robotics for Children

### 2023-03-11 slides/sources/air4children.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Xochicale M. 2014 \it{Libre Robotics (proposal)} }
\begin{frame}{Prototyping Open Source Robots}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Xochicale M. 2015 in Mecate; Parra C. et al. 2016, \it{Otto DIY}}
\begin{frame}{Piloting robot prototypes}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v01.png}
        %\caption{}
      \end{figure}
\end{frame}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
\begin{frame}{Adopting Montessori Education in the curriculum of AIR4Children } 
  \vspace{3mm}
  \it{"The hand is the instrument of the mind."} Dr. Maria Montessori (1970-1952).
  \vspace{2mm}
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

@@

  \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v02.png}
        %\caption{}
      \end{figure}
\end{frame}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Xochicale M. 2014 \it{Libre Robotics (proposal)} }
\begin{frame}{Prototyping Open Source Robots}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/air4children-a/outputs/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Xochicale M. 2015 in Mecate; Parra C. et al. 2016, \it{Otto DIY}}
\begin{frame}{Piloting robot prototypes}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/air4children-b/outputs/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
\begin{frame}{Adopting Montessori Education in the curriculum of AIR4Children } 
  \vspace{3mm}
  \it{"The hand is the instrument of the mind."} Dr. Maria Montessori (1970-1952).
  \vspace{2mm}
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/montessori/outputs/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}

@@

  \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/outputs/drawing-v02.png}
        %\caption{}
      \end{figure}
\end{frame}
}

### 2023-03-11 slides/sources/conclusions-future-work.tex

      \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{./figures/future-work/versions/drawing-v00.png}
      \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{./figures/team/versions/drawing-v00.png}
  \end{figure}

>>>>

      \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{./figures/logo/outputs/drawing-v00.png}
      \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{./figures/team/outputs/drawing-v00.png}
  \end{figure}

### 2023-03-11 slides/sources/introduction.tex
adds timeline-osh [skip-all]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The progress of AI and Robotics (AIR)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Savage N. 2021 in Nature}
\begin{frame}{The progress of AI and Robotics in USA, China and EU}
      \begin{figure}
        \centering
        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
        %\caption{}
      \end{figure}
\end{frame}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Savage N. 2021 in Nature}
\begin{frame}{Open source software and hardware in AIR}
      \begin{figure}
        \centering
        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
        %\caption{}
      \end{figure}
\end{frame}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Education, Investment and Publications in AI and Robotics (AIR)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 4.3.3 https://aiindex.stanford.edu/report/}

\begin{frame}{The progress of AI and Robotics in USA, China and EU}

\begin{figure}
 \centering
 \includegraphics[width=1.0\textwidth]{./figures/progress-of-air-a/outputs/drawing-v00.png}
 %\caption{}
\end{figure}

\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 1.1.19 https://aiindex.stanford.edu/report/}

\begin{frame}{The progress of AI and Robotics in USA, China and EU}

\begin{figure}
 \centering
 \includegraphics[width=1.0\textwidth]{./figures/progress-of-air-b/outputs/drawing-v00.png}
 %\caption{}
\end{figure}

\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 1.1.19 https://aiindex.stanford.edu/report/}

\begin{frame}{The progress of AI and Robotics in USA, China and EU}

\begin{figure}
 \centering
 \includegraphics[width=1.0\textwidth]{./figures/progress-of-air-c/outputs/drawing-v00.png}
 %\caption{}
\end{figure}

\end{frame}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
%\paper{Savage N. 2021 in Nature}
\begin{frame}{Open source software and hardware in AIR}

      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/timeline-osh/outputs/drawing-v00.png}
        %\caption{}
      \end{figure}
\end{frame}
}
